Active Contextual Entropy Search

### 2016-06-08 2016_ICML/poster/content/left_column.tex
Revising poster

\begin{block}{\blocktitle{Background}}
\textbf{Bayesian optimization} \cite{shahriari_taking_2016}:
\begin{itemize}
\item black-box optimization problems $\mathbf{x} = \arg\min_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
\item maintains a \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
\item decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next based on GP posterior of first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}
\item recommends $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
\item objective: minimize \emph{simple regret} 
$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$
\end{itemize}

@@

Minimum regret search (MRS): acquistion function based directly on external objective of minimizing simple regret
\begin{itemize}
 \item Expected simple regret: $\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
x})]$
 \item For fixed GP $p(f)$, $\arg\min_\mathbf{x} \text{ER}(p)(\mathbf{x})$ corresponds to the maximizer of the GP mean
 \item MRS aims at selecting query points s.t. ER is minimized also with respect to resulting $p(f)$
 \item Myopic choice: select next query point s.t. minimum ER is reduced the most (in expectation)
 \item $a_{\text{MRS}^{\text{point}}}(\mathbf{x}^q)
	= \min_{\mathbf{\tilde x}}\text{ER}(p_n)(\mathbf{\tilde x})
	 - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]$
 \item Additionally also account for uncertainty in minimizer $\mathbf{\tilde x}$ of $\text{ER}$ yields MRS
 \item $a_{\text{MRS}}(\mathbf{x}^q)
    = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}[\text{ER}(p_n)(\mathbf{\tilde x})] 
	   - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[
		  \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_{\mathcal{D}_n \cup \{(\mathbf{x}^q, y)\}}}[
			 \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]]$
\end{itemize}

Approximate $a_{\text{MRS}}$ based on sampling:
\begin{itemize}
 \item approximate $\mathbb{E}_{p(f)}$ by taking $n_f=1000$ Monte Carlo samples from $p(f)$
 \item approximate $\mathbb{E}_{y \vert p(f), \mathbf{x}^q}$  by taking
$n_y=51$ Monte Carlo samples from $p(f)$'s predictive distribution at
$\mathbf{x}_q$
 \item discretize $p^\star$ to a finite set of $n_r=25$ representer points (Thompson
sampling from $p(f)$ on candidate points)
 \item estimating $p^\star_{\mathcal{D}_n}$ on representer points by reusing the samples used 
for approximating $\mathbb{E}_{p(f)}$
\item Common random numbers in estimation of
$\text{ER}(p)(\mathbf{x})$ for different $p(f)$ reduces variance
\end{itemize}
\end{block}

>>>>

\begin{block}{\blocktitle{Background}}
\textbf{Bayesian optimization} \cite{shahriari_taking_2016}:
\begin{itemize}
\item black-box optimization problems $\mathbf{x} = \arg\max_{\mathbf{x} \in \mathcal{X}} f(x)$ of some function $f: \mathcal{X} \to \mathbb{R}$ on some bounded set $\mathcal{X} \subset \mathbb{R}^D$.
\item maintains a \emph{probabilistic model} $p(f)$ for $f(\mathbf{x})$, typically a Gaussian process (GP)
\item decides on a query point $\mathbf{x}_{n+1}$ where $f$ will be evaluated next based on GP posterior after first $n$ observations $\mathcal{D}_n=\{(\mathbf{x}_i, y_i)\}_{i=1}^n$ and an \emph{acquisition function}
\item recommends $\mathbf{\tilde x}_N$ after $N$ queries (optimum of GP or best query point)
\item objective: minimize \emph{simple regret} 
$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$
\end{itemize}

@@

Minimum regret search (MRS): acquistion function based directly on external objective of minimizing simple regret
\begin{itemize}
 \item Expected simple regret: $\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
x})]$
 \item For fixed GP $p(f)$, $\arg\min_\mathbf{x} \text{ER}(p)(\mathbf{x})$ corresponds to the maximizer of the GP mean
 \item MRS aims at selecting query points s.t.\  ER is minimized also with respect to resulting $p(f)$
 \item Myopic choice: select next query point s.t.\ minimum ER is reduced the most (in expectation)
 \item $a_{\text{MRS}^{\text{point}}}(\mathbf{x}^q)
	= \min_{\mathbf{\tilde x}}\text{ER}(p_n)(\mathbf{\tilde x})
	 - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[\min_{\mathbf{\tilde x}}  \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]$
 \item Additionally also accounting for uncertainty in minimizer $\mathbf{\tilde x}$ of $\text{ER}$ yields MRS
 \item $a_{\text{MRS}}(\mathbf{x}^q)
    = \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_{\mathcal{D}_n}}[\text{ER}(p_n)(\mathbf{\tilde x})] 
	   - \mathbb{E}_{y \vert p_n(f), \mathbf{x}^q}[
		  \mathbb{E}_{\mathbf{\tilde x} \sim p^\star_{\mathcal{D}_n \cup \{(\mathbf{x}^q, y)\}}}[
			 \text{ER}(p^{[\mathbf{x}^q, y]}_n)(\mathbf{\tilde x})]]$
\end{itemize}

Approximate $a_{\text{MRS}}$ based on sampling:
\begin{itemize}
 \item approximate $\mathbb{E}_{p(f)}$ by taking $n_f=1000$ Monte Carlo samples from $p(f)$
 \item approximate $\mathbb{E}_{y \vert p(f), \mathbf{x}^q}$  by taking
$n_y=51$ Monte Carlo samples from $p(f)$'s predictive distribution at
$\mathbf{x}_q$
 \item discretize $p^\star$ to a finite set of $n_r=25$ representer points (Thompson
sampling from $p(f)$ on candidate points)
 \item estimating $p^\star_{\mathcal{D}_n}$ on representer points by reusing the samples used 
for approximating $\mathbb{E}_{p(f)}$ (incurs a small bias)
\item Common random numbers in estimation of
$\text{ER}(p)(\mathbf{x})$ for different $p(f)$ reduces variance
\end{itemize}
\end{block}

### 2016-06-08 2016_ICML/poster/content/right_column.tex
Revising poster

\begin{block}{\blocktitle{Synthetic Single-Task Benchmark}}
\begin{itemize}
 \item Target functions sampled from a generative model (GP with isotropic RBF kernel
of length scale $l = 0.1$ and unit signal variance) on $\mathcal{X} = [0, 1]^2$ 
 \item In practice: sample $250$ function values from GP, fit GP to these function values and use resulting posterior mean as target function
 \item Gaussian noise with standard deviation $\sigma =10^{-3}$ is added to each observation
 \item Model mismatch: target functions from GP with rational quadratic kernel but RBF kernel in surrogate model
\end{itemize}

@@

\begin{block}{\blocktitle{Outlook}}
\begin{itemize}
 \item For multi-task MRS and results on simulated robotic task: see paper
 \item Open questions: treatment of GP hyperparameters, more efficient approximation techniques for MRS, regret bounds for MRS?
 \item Source code: \url{https://github.com/jmetzen/bayesian_optimization}
\end{itemize}
\end{block}

>>>>

\begin{block}{\blocktitle{Synthetic Single-Task Benchmark}}
\begin{itemize}
 \item Target functions sampled from a generative model (GP with isotropic RBF kernel
of length scale $l = 0.1$ and unit signal variance) on $\mathcal{X} = [0, 1]^2$ 
 \item In practice: sample $250$ function values from GP, fit GP to these function values, and use resulting posterior mean as target function
 \item Gaussian noise with standard deviation $\sigma =10^{-3}$ is added to each observation
 \item Model mismatch: target functions from GP with rational quadratic kernel but RBF kernel in surrogate model
\end{itemize}

@@

\begin{block}{\blocktitle{Outlook}}
\begin{itemize}
 \item For multi-task MRS and results on simulated robotic task: see paper
 \item Open questions: treatment of GP hyperparameters, more efficient approximation techniques for MRS, are there regret bounds for MRS?
 \item Source code: \url{https://github.com/jmetzen/bayesian_optimization}
\end{itemize}
\end{block}
